Scheduling and Vectorization for MPC

### 2022-04-08 overleaf/paper_SIMD.tex
Add LaTeX \benjamin command

\begin{enumerate}
  \item
        \textbf{Parsing}:
        Use Python's \texttt{ast} module to parse the input source code to a Python AST.
  \item
        \textbf{Syntax checking}:
        Ensure that the AST matches a restricted subset that our compiler supports.
        This step outputs an instance of the \texttt{restricted\_ast.Function} class, which represents our restricted subset of the Python AST.
  \item
        \textbf{3-address CFG conversion}:
        TODO: Is this a good amount of detail?

@@

>>>>

\begin{enumerate}
  \item
        \textbf{Parsing}:
        Use Python's \texttt{ast} module to parse the input source code to a Python AST.
  \item
        \textbf{Syntax checking}:
        Ensure that the AST matches a restricted subset that our compiler supports.
        This step outputs an instance of the \texttt{restricted\_ast.Function} class, which represents our restricted subset of the Python AST.
  \item
        \textbf{3-address CFG conversion}:
        \benjamin{TODO: Is this a good amount of detail?}

@@

Once the compiler converts the code to SSA,
it transforms $\phi$-nodes that correspond to if-statements into MUX nodes.
From the 3-address CFG conversion step,
$\phi$-nodes corresponding to if-statements will be in a basic block
with the ``merge condition'' property.
For example, if $X_3 = \phi(X_1,X_2)$ is in a block with merge condition $C$,
the compiler transforms it into $X_3 = \mathit{MUX}(C, X_1, X_2)$.
Next, the compiler runs the dead code elimination algorithm from Cytron's SSA paper.
Then, the control-flow graph is \emph{linearized} into MPC source,
which has loops but no if-statements.
\benjamin{TODO: Add more here}
